Extended Data

### 2022-03-04 doc/manuscript/Dow_manuscript_Nature.Rmd
tweaked data cleaning section
@camerondow35 , please confirm my change in line 368 to finalize this paragraph.

After fitting the growth model, we removed tree-years with poor fits. 
Models were judged to be poorly fit if certain modeled growth characteristics fell outside of the logical range. 
Modeled fits for tree-years were removed under five conditions:
<!--rearrange these in order of how data were removed (3 & 4 come first)-->
(1) ~~single day growth rates were~~ $g_{max}$ was <!--confirm this change--> $\ge 2.5$ standard deviations away from the mean for each xylem architecture (SCBI = 3, Harvard Forest = 11); 
(2) timing variables ($DOY_{ip}$, $DOY_{25}$, $DOY_{50}$, $DOY_{75}$) were $\ge 2.5$ standard deviations away from the means for their xylem architecture group, year, and site (SCBI = 74, Harvard Forest = 101).
At both sites the tag years removed through this method were proportional to the original sample size, indicating that no species or size class was disproportionately removed compared to others.
This process was repeated using 2 and 3 standard deviations and the results of analyses were not qualitatively different.

>>>>

After fitting the growth model, we removed tree-years with poor fits.
Models were judged to be poorly fit if modeled growth parameters were outliers, which were commonly indicative of unrealistic fits (e.g., growth occurring outside the growing season or over a very short period) and underlain by very slow tree growth or poor data records.
Modeled fits for tree-years were removed under two conditions:
(1) ~~single day growth rates were~~ $g_{max}$ was <!--confirm this change--> $\ge 2.5$ standard deviations away from the mean for each xylem architecture (SCBI = 3, Harvard Forest = 11); 
(2) timing variables ($DOY_{ip}$, $DOY_{25}$, $DOY_{50}$, $DOY_{75}$) were $\ge 2.5$ standard deviations away from the means for their xylem architecture group, year, and site (SCBI = 74, Harvard Forest = 101).
At both sites the tree-years removed through this method were proportional to the original sample size, indicating that no species or size class was disproportionately removed compared to others.
This process was repeated using 2 and 3 standard deviations as the cutoff for defining outliers, yielding qualitatively similar results.
